A tool for designing digital filters for the Hankel and Fourier transforms in potential, diffusive, and wavefield modeling

### 2019-03-08 DLF-in-Geophysics.tex
Update with final page numbers.

{\huge \bf \sffamily Digital Linear Filters in Geophysics\\[.5cm]}
{\small\emph{Excerpt from \cite{GEO.18.Werthmuller}; for the full article see
\href{https://github.com/empymod/article-fdesign}{github.com/empymod/article-fdesign}.}}

@@

\bibitem[Guptasarma and Singh, 1997]{GP.97.Guptasarma}
Guptasarma, D., and B. Singh,  1997, New digital linear filters for {H}ankel
  {J}0 and {J}1 transforms: Geophysical Prospecting, {\bf 45}, 745--762.
\newblock (\href{https://doi.org/10.1046/j.1365-2478.1997.500292.x}{doi:
  10.1046/10.1046/j.1365-2478.1997.500292.x}).

@@

\bibitem[Werthmüller et~al., 2018]{GEO.18.Werthmuller} Werthmüller, D., K. Key,
  and E. Slob, 2018, A tool for designing digital filters for the Hankel and
  Fourier transforms in potential, diffusive, and wavefield modeling:
  Geophysics, {\bf 83}, no. ?, ????--????.
\newblock (\href{https://doi.org/10.1190/geo2018-0069.1}{doi:
  10.1190/geo2018-0069.1}).

>>>>

{\huge \bf \sffamily Digital Linear Filters in Geophysics\\[.5cm]}
{\small\emph{Excerpt from \cite{GEO.19.Werthmuller}; for the full article see
\href{https://github.com/empymod/article-fdesign}{github.com/empymod/article-fdesign}.}}

@@

\bibitem[Guptasarma and Singh, 1997]{GP.97.Guptasarma}
Guptasarma, D., and B. Singh,  1997, New digital linear filters for {H}ankel
  {J}0 and {J}1 transforms: Geophysical Prospecting, {\bf 45}, 745--762.
\newblock (\href{https://doi.org/10.1046/j.1365-2478.1997.500292.x}{doi:
  10.1046/j.1365-2478.1997.500292.x}).

@@

\bibitem[Werthmüller et~al., 2019]{GEO.19.Werthmuller} Werthmüller, D., K. Key,
  and E. Slob, 2019, A tool for designing digital filters for the Hankel and
  Fourier transforms in potential, diffusive, and wavefield modeling:
  Geophysics, {\bf 84}, no. 2, F47--F56.
\newblock (\href{https://doi.org/10.1190/geo2018-0069.1}{doi:
  10.1190/geo2018-0069.1}).
